Simple and robust inference of connectomes using partial correlation coefficients

### 2014-06-10 article.tex
FIX compilation
some small changes

%\paragraph{Motivation\\} Intuitively, connectivity information between two
neurons may be retrieved from successive and slightly delayed burst events. In
case of a directed relationship, the burst order should be the same while in
case of an undirected relationship, it could change. Therefore, the
fluorescent signal can be reduced to a binary signal representing the activity
of a neuron. This is the idea behind the filter $g_1$:  \begin{align}
g_1^q(X^i_t) = (X^i_t)^{0.9} \mathbb{1}(X^i_t \ge q) \end{align} where ... .

Considering the short delay for a communication between neurons, slow events
can be neglected to retrieve direct relationships. Note that the average time
delay is about $1ms$ or $2ms$ while the fluorescent signal time resolution is
$20ms$. Let us also highlight that even if two neurons are spatially far from
each other, the information is expected in the same time step or at most in
the next time step. It is therefore not necessary to keep low-frequency event
and we thus apply a high-pass filter $g_2$: \begin{align} g_2^k(X^i_t) =
\sum_{l=-3}^{2} c^k_l X^i_{t+l}  \end{align} where ... .

However, the signal, by the imaging capture process we suppose, is very noisy.
A low-pass filter seems a good way to smooth the signal and only keep relevant
informations. We thus choose to consider the discrete derivative of the signal
$g_3$: \begin{align} g_3(X_t^i) = X^i_t - X^i_{t-1} \end{align} where ... .

% We then define our preprocessing function $G$ as
% \begin{align}
% G(X_t^i) = g^q_1(g_3(g_2(X_t^i))).
% \end{align}

@@

where $r(x)$ is a 4-piecewise continuous functions whose parameters were tuned
for each low-pass filter.

@@

Hence, we define our preprocessing function $G$ as 
\begin{align}
G^{q,k}(X_t^i) = h_2 \bullet h_1 \bullet g^q_1 \bullet g_3 \bullet g_2^k(X_t^i).
\end{align}

@@

\textcolor{red}{Motivation pour l'inverse : retirer les liens indirects.
\Pareil: proposition de AS  et certains choses pourraient être incorporées
\dans la version de AJ.}

@@

Let us consider see neurons as random variables $\mathcal{X}_i$ which follows
a probability density function $p_{\mathcal{X}_i}$ and let us denote by
$p_{\mathcal{X}_i,\mathcal{X}_j|\mathcal{Z}}$ the joint probability
distribution between neurons $i$ and $j$ conditioned on a subset of neurons
$\mathcal{Z}$ (eventually empty). Let us define $\mathcal{V}$ the set of all
neurons $\mathcal{X}_1, \dots, \mathcal{X}_p$, and by $\mathcal{V}^{i,j}$ the
same set without neurons $\mathcal{X}_i$ and $\mathcal{X}_j$.

 First, if we want to highlight
relationships between without considering the distinction between direct and
indirect links, the Pearson correlation matrix, i.e. each element $(i,j)$ of a
such matrix is the correlation coefficient between neurons $\mathcal{X}_i$ and $\mathcal{X}_j$.

>>>>

%\paragraph{Motivation\\} 
Intuitively, connectivity information between two
neurons may be retrieved from successive and slightly delayed burst events. In
case of a directed relationship, the burst order should be the same while in
case of an undirected relationship, it might change. Therefore, the
fluorescent signal can be reduced to a binary signal representing the activity
of a neuron. This is the idea behind the filter $g_1$:  \begin{align}
g_1^q(X^i_t) = (X^i_t)^{0.9} \mathbb{1}(X^i_t \ge q) \end{align} where ... .

Considering the short delay for a communication between neurons, slow events
can be neglected to retrieve direct relationships. Note that the average time
delay is about $1ms$ or $2ms$ while the fluorescent signal time resolution is
$20ms$. Let us also highlight that even if two neurons are spatially far from
each other, the information is expected in the same time step or at most in
the next time step. It is therefore not necessary to keep low-frequency event
and we thus choose to consider the discrete derivative of the signal, i.e. a
high-pass filtered version, $g_2$:  \begin{align} g_2(X_t^i) = X^i_t -
X^i_{t-1} \end{align} where ... .

However, the signal, by the imaging capture process we suppose, is very noisy.
A low-pass filter seems a good way to smooth the signal and only keep relevant
informations. We thus apply the filter
$g_3$: 
\begin{align} g_3^k(X^i_t) =
\sum_{l=-3}^{2} c^k_l X^i_{t+l}  \end{align} where ... .
% We then define our preprocessing function $G$ as
% \begin{align}
% G(X_t^i) = g^q_1(g_3(g_2(X_t^i))).
% \end{align}

@@

\textcolor{red}{miss the case where activity < 0->1} where $r(x)$ is a 4-piecewise continuous functions whose parameters were tuned
for each low-pass filter.

@@

Hence, we define our preprocessing function $G$ as
\begin{align}
G^{q,k}(X_t^i) = h_2 \bullet h_1 \bullet g^q_1 \bullet g_2 \bullet g_3^k(X_t^i).
\end{align}

Finally since there is a high correlation between neurons, we made a
low-rank hypothesis and perform noise filtering through a principal component
approach [TODO cite]. From the $p$ eigen vectors, we only kept $80\%$ of
the eigen vectors which have the largest eigen value \textcolor{red}{fig?}.

@@

\textcolor{red}{Motivation pour l'inverse : retirer les liens indirects.
Pareil: proposition de AS  et certains choses pourraient être incorporées
dans la version de AJ.}

@@

Let us consider the neurons as random variables $\mathcal{X}_i$ which follows
a probability density function $p_{\mathcal{X}_i}$ and let us denote by
$p_{\mathcal{X}_i,\mathcal{X}_j|\mathcal{Z}}$ the joint probability
distribution between neurons $i$ and $j$ conditioned on a subset of neurons
$\mathcal{Z}$ (eventually empty). Let us define $\mathcal{V}$ the set of all
neurons $\mathcal{X}_1, \dots, \mathcal{X}_p$, and by $\mathcal{V}^{i,j}$ the
same set without neurons $\mathcal{X}_i$ and $\mathcal{X}_j$.

% Without considering indirect/direct --> Correlation matrix

First, if we want to highlight relationships between neurons without
considering the distinction between direct and indirect links, the Pearson
correlation matrix, i.e. each element $(i,j)$ of a such matrix is the
correlation coefficient between neurons $\mathcal{X}_i$ and $\mathcal{X}_j$, can computed.

% However, we only want direct links --> partial correlation
